### 2020-05-27 8_case_study.tex
More edits on case study.

Initial experiments with TensorFlow revealed that the TensorFlow Task
Bench implementation was not able to use all cores on a node (thus
making it impossible to measure METG since the efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.

>>>>

Initial experiments with TensorFlow revealed that the Task
Bench implementation was not able to use all cores on a node (making it impossible to measure METG since efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.
